01_Vegetation_cover

### 2022-08-19 01_Species_abundance.Rmd
fix pattern matching issue

```{r standardize species names}
harm <- read_xlsx("Data/Harmonization_table_species_names.xlsx") 
spec_a <- spec_a %>% 
  left_join(harm, by = "species")
veg_cover_bc <- veg_cover_bc %>% 
  left_join(harm, by = "species")

>>>>

```{r standardize species names}
# load in generalized species list, spelling checked and harmonized with
# LCVP
harm <- read_xlsx("Data/Harmonization_table_species_names.xlsx") 
harm <- harm %>% 
  mutate(stand.spec = str_remove(stand.spec, pattern = " sp\\."))
spec_a <- spec_a %>% 
  left_join(harm, by = "species")
veg_cover_bc <- veg_cover_bc %>% 
  left_join(harm, by = "species")
